### 2024-04-05 doc/15yrsChange.Rmd
data availability statement
@llmorreale , ideally we'll want to make this repo public today. Once it's public, we can archive in Zenodo, which will assign a DOI (which can refer to all versions). We'll want to clean it up before archiving in Zenodo.

# Data availability {-#Data}

>>>>

# Data and code availability {-#Data}

All data and code supporting this analysis are available via the public GitHub repository "15yrsChange" within the SCBI-ForestGEO organization (https://github.com/SCBI-ForestGEO/15yrsChange) and archived in Zenodo (DOI: TBD)<!--this can be obtained once the repo is made public-->.
The most up-to-date versions of the data products analyzed here are publicly available via the ForestGEO data portal (https://forestgeo.si.edu/explore-data) and the SCBI-ForestGEO GitHub organization (https://github.com/SCBI-ForestGEO).
